The Hypothesis of Testing: Paradoxes arising out of reported coronavirus case-counts

### 2020-04-20 write-up/covid-writeup.tex
Update covid-writeup.tex

\subsection{Imperfect tests and }

Meng's analysis is critical when selection bias is present.  For the current crisis, the analysis should be extended in two directions.  First, tests are imperfect. Measurement-error.

Let $P_j$ be an indicator that equals 1 when we observe reverse of the true outcome and equals 0 when we observe the true outcome. We suppose this is a stochastic variable that satisfies $\pr(P_j = 1 \mid Y_j = 1) =: FN$ is the false-negative rate and $\pr(P_j = 1 \mid Y_j = 0) =: FP$ is the false-positive rate.  If individual $j$ is selected (i.e., $I_j = 1$) then the  $Y_j^\star = Y_j(1-P_j) + (1-Y_j) P_j$.

@@

This is quite complex but he main point is that the sign of the new terms can be either positive or negative.  Moreover, there is an interaction between...
This means that raw application is, of course, biased but the expected bias directionality is not guaranteed.  There's a clear interaction between selection bias, measurement-error, prevalence, and data quantity!

To see this

@@

@@

>>>>

\subsection{Imperfect testing}

Tests are imperfect.  COVID-19 testing is no exception.  State-level case-count data is often used to signify disease prevalence per state.  When assessing prevalence in a community, sensitivity (true positive rate) and specificity (true negative rate) must be taken into account.  Here we investigate the interplay between imperfect testing and selection bias.  The standard story of ``measurement-error leads to parameter attenuation'' does not pan out.  Instead, the two sources of error become entangled, and the biases can become magnified, muted, or even switch signs.

First we require some additional notation.  Let $P_j$ be an indicator of measurement error, equal to $1$ when we mismeasure the outcome and $0$ when we observe the true outcome. We suppose this is a stochastic variable that satisfies $\pr(P_j = 1 \mid Y_j = 1, I_j = 1) =: FN$ is the false-negative rate and $\pr(P_j = 1 \mid Y_j = 0, I_j = 1) =: FP$ is the false-positive rate.  If individual $j$ is selected (i.e., $I_j = 1$) then the observed outcome can be written as $Y_j^\star = Y_j(1-P_j) + (1-Y_j) P_j$.

@@

This is quite complex but he main point is that the sign of the new terms can be either positive or negative.  Moreover, there is an interaction between...
This means that raw application is, of course, biased but the expected bias directionality is not guaranteed.  There's a clear interaction between selection bias, measurement-error, prevalence, and data quantity!
We are not the first to note this, but  (twitter guy) for a longer discussion of additional myths related

 critical when selection bias is present.  For the current crisis, the analysis should be extended in two directions.  First, tests are imperfect. Measurement-error.

In addition, testing quality is likely to be a dynamic process.  The US is keen to increase testing.  Commentators have requested expedited FDA approval for variations on the currently available tests to speed up production.  This is likely to increase testing inaccuracies.  The bias and MSE depend on interaction among specificity,

@@

\begin{itemize}
\item Simulation study showing that $R_t$ and prevalence over time changes the effective sample size....
\end{itemize}

@@

\subsection{Stratified sampling: improving precision in low-prevalence environments}

Sampling network is hard.  Sampling high-risk strata is easy.  Simple example.
DTR and network connectivity is useful for understanding spread and where "testing should go".
